---
title: "kaggle_3"
author: "Siming Yan"
date: "2/19/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

<!-- ## R Markdown -->
 

```{r cars, message = F, warning = F}

library(caret)
library(tidyverse)
library(xgboost)
library("Matrix")
```

```{r}
train_data = read.csv("./encoded_train.csv")
tests_data = read.csv("./encoded_test.csv")
train_y    = read.csv("./trian_y.csv")
sub = read.csv("./sample_submission.csv")
```

```{r}
View(train_data %>% head())
```

```{r}
cols.cat <- paste0("cat", c(0:18))
train_data[cols.cat] <- lapply(train_data[cols.cat], as.factor)
# delete survived
tests_data[cols.cat] <- lapply(tests_data[cols.cat], as.factor)
# train = train_data
# train_data = train
# tests = tests_data
#--------------------------------------------
set.seed(9111)
index = sample(c(1:300000), .75*300000)
samplesize = 0.75 * nrow(train_data)
# index0 = sample(nrow(train_data),size = samplesize)

train_df  = train_data[index, ]
train_label = train_y[index, ]
valid_df  = train_data[-index, ] 
valid_label = train_y[-index, ]
```

```{r}
train_data_xgb = xgb.DMatrix(as(as.matrix(train_df), "dgCMatrix"), 
                             label = train_label) # dtrain
valid_data_xgb = xgb.DMatrix(as(as.matrix(valid_df), "dgCMatrix"), 
                             label = valid_label)
test_data_xgb  = xgb.DMatrix(as(as.matrix(tests_data), "dgCMatrix"),
                             label = rep(0, dim(tests_data)[1]) %>% as.factor())
```

```{r}
# library(parallel)
# library(parallelMap) 
# parallelStartSocket(cpus = detectCores())
```

# xgboosting with xgb

```{r}
watchlist <- list(eval = valid_data_xgb, train = train_data_xgb)

xgb = xgb.train(
  params = list(max_depth=c(7, 9, 11, 13, 15),
                eta = c(.01, .1, 1),
                subsample = .75,
                # sampling_method = "gradient_based", 
                # lambda = c(.25, .5, .75, 1),
                # gamma = c(0, 0.25, 0.5),
                eval_metric = 'auc', 
                # alpha = c(.25, .5, .75, 1),
                # max_bin = 1024
                n_estimators = c(200, 400, 700, 1000)
                ),
  # booster=dart,
  objective = "reg:logistic",
  data = train_data_xgb,
  nrounds = 250,
  verbose = 1,
  print_every_n = 3L,
  early_stopping_rounds = 20,
  save_name = "xgboost.model",
  watchlist
  # xgb_model = NULL
)
```


```{r}
xgb$best_msg
# "[150]\teval-auc:0.876067\ttrain-auc:0.885645" ongoing up!
xgb.save(xgb, "./XGB_xgboost.model")
```

```{r}
pred_XGB = predict(xgb, test_data_xgb)
sub$target =pred_XGB
write.csv(sub, "./submission_R_XGB.csv", index = F)
```


```{r}
mat <- xgb.importance (feature_names = colnames(train_data),model = xgb)
xgb.plot.importance (importance_matrix = mat[1:20]) 
```

#--------------------------------------------
## caret tune

```{r}
library(caret)
train_data %>% dim # [1] 300000     30
train_y %>% dim #  300000

x_train = train_data
y_train = train_y$target %>% as.factor()
```

```{r}
normalizedGini <- function(aa, pp) {
    Gini <- function(a, p) {
        if (length(a) !=  length(p)) stop("Actual and Predicted need to be equal lengths!")
        temp.df <- data.frame(actual = a, pred = p, range=c(1:length(a)))
        temp.df <- temp.df[order(-temp.df$pred, temp.df$range),]
        population.delta <- 1 / length(a)
        total.losses <- sum(a)
        null.losses <- rep(population.delta, length(a)) # Hopefully is similar to accumulatedPopulationPercentageSum
        accum.losses <- temp.df$actual / total.losses # Hopefully is similar to accumulatedLossPercentageSum
        gini.sum <- cumsum(accum.losses - null.losses) # Not sure if this is having the same effect or not
        sum(gini.sum) / length(a)
    }
    Gini(aa,pp) / Gini(aa,aa)
}

# create the normalized gini summary function to pass into caret
giniSummary <- function (data, lev = "Yes", model = NULL) {
    levels(data$obs) <- c('0', '1')
    out <- normalizedGini(as.numeric(levels(data$obs))[data$obs], data[, lev[2]])  
    names(out) <- "NormalizedGini"
    out
}

# create the training control object. Two-fold CV to keep the execution time under the kaggle
# limit. You can up this as your compute resources allow. 
trControl = trainControl(
    method = 'cv',
    number = 5,
    # summaryFunction = giniSummary,
    classProbs = TRUE,
    verboseIter = TRUE,
    allowParallel = TRUE)

# create the tuning grid. Again keeping this small to avoid exceeding kernel memory limits.
# You can expand as your compute resources allow. 
# tune_grid <- expand.grid(
#   nrounds = seq(from = 200, to = nrounds, by = 50),
#   eta = c(0.025, 0.05, 0.1, 0.3),
#   max_depth = c(2, 3, 4, 5, 6),
#   gamma = 0,
#   colsample_bytree = 1,
#   min_child_weight = 1,
#   subsample = 1
# )
tuneGridXGB <- expand.grid(
    nrounds = c(10),
    max_depth = c(12),
    eta = c(0.05, 0.1),
    gamma = c(0.01),
    colsample_bytree = c(0.75),
    subsample = c(0.750),
    min_child_weight = c(0))
```

```{r}
caret_tune_data = cbind(x_train, y_train)
cat_col = (caret_tune_data %>% names())[1:19]
caret_tune_dada = fastDummies::dummy_cols(caret_tune_data, select_columns = cat_col)
caret_tune_dada = caret_tune_dada[, 20:ncol(caret_tune_dada)]
# caret_tune_fi = caret_tune_dada %>% data.frame() %>% cbind(caret_tune_data[,20:30])

levels(y_train) <- c("No", "Yes")
caret_tune_dada = caret_tune_dada[, !(names(caret_tune_dada) %in% "y_train")]
caret_tune_dada %>% str()
#--------------------------------------------
caret_test_dada = fastDummies::dummy_cols(tests_data, select_columns = cat_col)
caret_test_dada = caret_test_dada[, 20:ncol(caret_test_dada)]
```

```{r}
library(doParallel)
cl <- makePSOCKcluster(8)
registerDoParallel(cl)
# save.image("./based_tune_caret.RData")
```

```{r}
start <- Sys.time()

# train the xgboost learner
xgbmod <- train(
    x = caret_tune_dada,
    y = y_train,
    method = 'xgbTree',
    metric = "roc",
    # metric = 'NormalizedGini',
    trControl = trControl,
    tuneGrid = tuneGridXGB,
    verbose = T)


print(Sys.time() - start)

```

```{r}
rm_test = names(caret_test_dada)[!names(caret_test_dada) %in% names(caret_tune_dada)]
ad_test = names(caret_tune_dada)[!names(caret_tune_dada) %in% names(caret_test_dada)]

caret_test_dada = caret_test_dada[, !names(caret_test_dada) %in% rm_test]
#--------------------------------------------

ad_test %>% length
caret_test_dada %>% dim
dfbind = do.call(data.frame, replicate(12, rep(0, 200000), simplify=FALSE))
names(dfbind) = ad_test
caret_test_dada = cbind(caret_test_dada, dfbind)
caret_test_dada2 = caret_test_dada[,names(caret_tune_dada)]
#--------------------------------------------
preds <- predict(xgbmod, newdata = caret_test_dada2, type = "prob")

```


```{r}
preds %>% head()
sub$target = preds$Yes
write.csv(sub, "./sub_xgb_untune_method1.csv")
# write.csv(sub, "./submission_R_XGB.csv", index = F)
```

#--------------------------------------------

## caret tune 2

```{r}
# input_x <- as.matrix(select(tr_treated, -SalePrice_clean))
# input_y <- tr_treated$SalePrice_clean

input_x <- as.matrix(caret_tune_dada)
input_y <- y_train
```


```{r}
# run with default paras 
grid_default <- expand.grid(
  nrounds = 10,
  max_depth = 6,
  eta = 0.3,
  gamma = 0,
  colsample_bytree = 1,
  min_child_weight = 1,
  subsample = 1
)

train_control <- caret::trainControl(
  method = "none",
  verboseIter = F, # no training log
  allowParallel = TRUE # FALSE for reproducible results 
)

xgb_base <- caret::train(
  x = input_x,
  y = input_y,
  trControl = train_control,
  tuneGrid = grid_default,
  method = "xgbTree",
  verbose = TRUE
)
 
```

#--------------------------------------------
# Grid Search

## 1. Number of Iterations and the Learning Rate

```{r}
nrounds = 200
# note to start nrounds from 200, as smaller learning rates result in errors so
# big with lower starting points that they'll mess the scales
tune_grid <- expand.grid(
  nrounds = seq(from = 100, to = nrounds, by = 50),
  eta = c(0.025, 0.05, 0.1, 0.3),
  max_depth = c(4, 5, 6),
  gamma = 0,
  colsample_bytree = 1,
  min_child_weight = 1,
  subsample = 1
)

tune_control <- caret::trainControl(
  method = "cv", # cross-validation
  number = 3, # with n folds 
  #index = createFolds(tr_treated$Id_clean), # fix the folds
  verboseIter = FALSE, # no training log
  allowParallel = TRUE # FALSE for reproducible results 
)

xgb_tune <- caret::train(
  x = input_x,
  y = input_y,
  trControl = tune_control,
  tuneGrid = tune_grid,
  method = "xgbTree",
  verbose = TRUE
)
```


```{r}
# helper function for the plots
tuneplot <- function(x, probs = .90) {
  ggplot(x) +
    coord_cartesian(ylim = c(quantile(x$results$RMSE, probs = probs), min(x$results$RMSE))) +
    theme_bw()
}

tuneplot(xgb_tune)
```

## 2: Maximum Depth and Minimum Child Weight

```{r}
tune_grid2 <- expand.grid(
  nrounds = seq(from = 50, to = nrounds, by = 50),
  eta = xgb_tune$bestTune$eta,
  max_depth = ifelse(xgb_tune$bestTune$max_depth == 2,
    c(xgb_tune$bestTune$max_depth:4),
    xgb_tune$bestTune$max_depth - 1:xgb_tune$bestTune$max_depth + 1),
  gamma = 0,
  colsample_bytree = 1,
  min_child_weight = c(1, 2, 3),
  subsample = 1
)

xgb_tune2 <- caret::train(
  x = input_x,
  y = input_y,
  trControl = tune_control,
  tuneGrid = tune_grid2,
  method = "xgbTree",
  verbose = TRUE
)

tuneplot(xgb_tune2)
```

## 3. Column and Row Sampling
Based on this, we can fix minimum child weight to 3 and maximum depth to 3. Next, we’ll try different values for row and column sampling:

```{r}
tune_grid3 <- expand.grid(
  nrounds = seq(from = 50, to = nrounds, by = 50),
  eta = xgb_tune$bestTune$eta,
  max_depth = xgb_tune2$bestTune$max_depth,
  gamma = 0,
  colsample_bytree = c(0.4, 0.6, 0.8, 1.0),
  min_child_weight = xgb_tune2$bestTune$min_child_weight,
  subsample = c(0.5, 0.75, 1.0)
)

xgb_tune3 <- caret::train(
  x = input_x,
  y = input_y,
  trControl = tune_control,
  tuneGrid = tune_grid3,
  method = "xgbTree",
  verbose = TRUE
)

tuneplot(xgb_tune3, probs = .95)
```

## 4. Gamma

```{r}
tune_grid4 <- expand.grid(
  nrounds = seq(from = 50, to = nrounds, by = 50),
  eta = xgb_tune$bestTune$eta,
  max_depth = xgb_tune2$bestTune$max_depth,
  gamma = c(0, 0.05, 0.1, 0.5, 0.7, 0.9, 1.0),
  colsample_bytree = xgb_tune3$bestTune$colsample_bytree,
  min_child_weight = xgb_tune2$bestTune$min_child_weight,
  subsample = xgb_tune3$bestTune$subsample
)

xgb_tune4 <- caret::train(
  x = input_x,
  y = input_y,
  trControl = tune_control,
  tuneGrid = tune_grid4,
  method = "xgbTree",
  verbose = TRUE
)

tuneplot(xgb_tune4)
```

## 5: Reducing the Learning Rate
Now, we have tuned the hyperparameters and can start reducing the learning rate to get to the final model:

```{r}
tune_grid5 <- expand.grid(
  nrounds = seq(from = 600, to = 10000, by = 100),
  eta = c(0.01, 0.015, 0.025, 0.05, 0.1),
  max_depth = xgb_tune2$bestTune$max_depth,
  gamma = xgb_tune4$bestTune$gamma,
  colsample_bytree = xgb_tune3$bestTune$colsample_bytree,
  min_child_weight = xgb_tune2$bestTune$min_child_weight,
  subsample = xgb_tune3$bestTune$subsample
)

xgb_tune5 <- caret::train(
  x = input_x,
  y = input_y,
  trControl = tune_control,
  tuneGrid = tune_grid5,
  method = "xgbTree",
  verbose = TRUE
)

tuneplot(xgb_tune5)

```

## fit the model with best paras

```{r}
(final_grid <- expand.grid(
  nrounds = xgb_tune5$bestTune$nrounds,
  eta = xgb_tune5$bestTune$eta,
  max_depth = xgb_tune5$bestTune$max_depth,
  gamma = xgb_tune5$bestTune$gamma,
  colsample_bytree = xgb_tune5$bestTune$colsample_bytree,
  min_child_weight = xgb_tune5$bestTune$min_child_weight,
  subsample = xgb_tune5$bestTune$subsample
))
```

```{r}
(xgb_model <- caret::train(
  x = input_x,
  y = input_y,
  trControl = train_control,
  tuneGrid = final_grid,
  method = "xgbTree",
  verbose = TRUE
))
```

